### 2014-03-05 src/methodology.Rnw
update

The basic statement deletion was mdeled on the work by Deng et al.~\cite{deng2013empirical}. The operations
on single statements was modeled using \textit{VOID-M-CALLS,NONV-M-CALLS,CONSTR-CALLS,E-MEMBER-VAR,RM-INCR} for simple statements, and using \textit{RM-COND} for control structures, which replaced the boolean condition with false, resulting in removal of the block of statements. The operator for return values was modeled using \textit{RETURN-VALS}, which is similar.
The operators for \textit{while,for}, and \textit{if} statements were modeled using \textit{DELETE-COND}, which replaced the boolean condition with true, which removed the effect of conditional. The \textit{switch} statement deletion was modeled using \textit{RM-SWITCH} which replaced the first 100 labels with default label, resulting in the switch element getting deleted. (Due to the constraints of the architecture of PIT only the first 100 labels were replaced).
\subsection{Probes}

>>>>

The basic statement deletion was mdeled on the work by Deng et al.~\cite{deng2013empirical}. The operations
on single statements was modeled using \textit{VOID-M-CALLS,NONV-M-CALLS,CONSTR-CALLS,E-MEMBER-VAR,RM-INCR} for simple statements, and using \textit{RM-COND} for control structures, which replaced the boolean condition with false, resulting in removal of the block of statements. The operator for return values was modeled using \textit{RETURN-VALS}, which is similar.
The operators for \textit{while,for}, and \textit{if} statements were modeled using \textit{DELETE-COND}, which replaced the boolean condition with true, which removed the effect of conditional. The \textit{switch} statement deletion was modeled using \textit{RM-SWITCH} which replaced the first 100 labels with default label, resulting in the switch element getting deleted. (Due to the constraints of the architecture of PIT only the first 100 labels were replaced). The \textit{try catch} was not necessary at bytecode level.
Finally, to get an accurate estimation of the effect of true statement deletion, we grouped the mutants by line, and considered a single virtual mutant (That is, the total number of mutants is equal to the total number of lines). Further, killing any mutant from a line resulted in marking the virtual mutant for that line as killed. This gave us the mutation score for the virtual statement deletion operator.
We note that the approximation of simple statement deletion, especially when arithmetic operators are involved is not complete. However, as seen in Figure~\ref{fig:op}, the number of mutants produced by \textit{MATH} operator is very small. We also note that our approximation does not account for the increase in ease of detection when multiple mutations are combined together (ref: coupling effect). This also means that not all the lines may be mutated since there may be no applicable operators. However, given the constraints of a bytecode based mutation system, we believe that our procedure is reasonable.

\subsection{Probes}
